%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV of Nguyễn Phạm Gia Huy
% Revised with all vertical space removed.
% To be compiled with XeLaTeX.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt]{article}

%---------- Packages ----------
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

%---------- Global Line Height ----------
\linespread{1.0}

%---------- Font ----------
\setmainfont{Calibri}

%---------- Colors & Hyperlinks ----------
\definecolor{darkgray}{gray}{0.25}
\definecolor{linkcolor}{HTML}{000000}

\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor,
    pdftitle={CV - Nguyễn Phạm Gia Huy},
    pdfauthor={Nguyễn Phạm Gia Huy},
}

%---------- Layout & Spacing (MODIFIED FOR NO VERTICAL SPACE) ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt} % Removes space between paragraphs
\raggedbottom % Prevents vertical stretching of content on the page

%---------- Section Formatting ----------
\titleformat{\section}
  {\Large\bfseries\color{darkgray}\centering}
  {}
  {0em}
  {\MakeUppercase}
  []

\titlespacing*{\section}
  {0pt}
  {0pt}
  {0pt}

% --- REMOVE PAGE NUMBERS ---
\pagestyle{empty}

%---------- Document ----------
\begin{document}

%---------- Header ----------
{\centering
    {\Huge \bfseries Nguyễn Phạm Gia Huy} \\
    \vspace{4pt}
    \normalsize\href{mailto:yuh.nguyenpham@gmail.com}{yuh.nguyenpham@gmail.com} •
    \normalsize\href{https://linkedin.com/in/nguyenphamgiahuy}{linkedin.com/in/nguyenphamgiahuy} •
    \normalsize\href{https://github.com/NgnPhamGiaHuy}{github.com/NgnPhamGiaHuy} •
    \normalsize0969 122 412
}
\vspace{4pt}
%---------- Professional Summary ----------
\section*{Professional Summary}
A proactive and enthusiastic Information Technology graduate with a solid foundation in Object-Oriented Programming (OOP), database principles, and full-stack web development. Eager to apply strong logical thinking and problem-solving skills gained from hands-on project experience with JavaScript, Python, and RESTful APIs to contribute to a dynamic software engineering team. A fast learner dedicated to continuous professional growth and mastering new technologies.

%---------- Education ----------
\section*{Education}
\textbf{International University} \hfill Ho Chi Minh City, Vietnam \\
\textit{Engineer in Information Technology} \hfill 2019 – 2024

%---------- Experience ----------
\section*{Experience}
\textbf{CÔNG TY TNHH CÔNG NGHỆ TRUYỀN THÔNG CÁNH CAM} \hfill Ho Chi Minh City, Vietnam \\
\textit{Front-end Developer Intern} \hfill Aug 2024 – Nov 2024
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Collaborated within an Agile team to develop and deploy responsive web applications, working closely with designers and backend developers to streamline workflows.
    \item Integrated RESTful APIs using JavaScript to enable dynamic content rendering and ensure smooth client-side data interactions.
    \item Converted Figma prototypes into responsive, cross-browser interfaces using HTML, CSS, and JavaScript, demonstrating strong UI/UX awareness.
    \item Customized and optimized WordPress themes to align with client requirements, improving usability and maintaining brand consistency.
\end{itemize}

%---------- Projects ----------
\section*{Personal Projects}
\textbf{\href{https://github.com/NgnPhamGiaHuy/recial-social-media-platform}{Recial – A modern social media platform}}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Engineered a comprehensive, full-stack social media application featuring real-time communication, content sharing, and community management functionalities, designed for scalability and a seamless user experience.
    \item Developed a secure and scalable backend using Node.js and Express.js, designing RESTful APIs and MongoDB schemas to manage users, posts, groups, and media content efficiently.
    \item Implemented a robust authentication system supporting both JWT-based credentials and Google OAuth, ensuring secure access control across the platform.
    \item Built a dynamic, responsive frontend with Next.js and React, utilizing Redux for centralized state management to create a seamless and interactive user interface.
    \item Integrated WebSockets to power a real-time messaging and notification system, enabling instant communication and user engagement.
    \item Leveraged Firebase Storage for scalable and efficient handling of user-generated media uploads, including images and videos.
\end{itemize}
\textbf{\href{https://github.com/NgnPhamGiaHuy/media-crawler}{Media Crawler – Fast, safe, and sessionized website media extractor}}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Designed and developed a high-performance web application to crawl websites and intelligently extract, process, and cache media content (images, videos, audio) through a user-friendly interface.
    \item Engineered an asynchronous crawling engine using Python and aiohttp within a Flask framework, processing multiple pages concurrently to reduce media extraction times by up to 75\%.
    \item Implemented a sophisticated parsing module with Beautiful Soup to analyze HTML, CSS, and JSON, increasing media discovery rates by up to 40\% compared to standard extraction methods.
    \item Developed an intelligent media processing pipeline that automatically generates rich previews, such as video frames and audio waveforms, to enhance the user's browsing experience.
    \item Architected a robust, session-based caching system to optimize server performance and disk usage, featuring automated cleanup of expired assets and ensuring data isolation in a multi-user environment.
\end{itemize}
\textbf{\href{https://github.com/NgnPhamGiaHuy/google-cse-serp-extractor}{Google CSE SERP Extractor – Bulk Google results to clean files}}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Developed a production-grade data extraction tool that leverages Google's Custom Search Engine API to provide reliable, scalable SERP data for SEO and market research, bypassing common web scraping limitations.
    \item Engineered a high-throughput extraction engine to process thousands of keywords via Google's CSE API, implementing intelligent rate limiting, caching, and automated retries to ensure data integrity and maximize efficiency.
    \item Developed a dual-interface system with a FastAPI web application for interactive use and a CLI for automation, ensuring flexible workflows with multi-format data support (CSV, Excel, JSON).
    \item Implemented advanced query targeting to filter results from over 50 platforms (e.g., LinkedIn, GitHub), enabling precise data collection for competitive analysis and profile sourcing.
    \item Architected a production-ready system with robust error handling, centralized logging, and an automated API token manager that utilizes backup keys to manage quotas and guarantee uninterrupted operation.
\end{itemize}
\textbf{\href{https://github.com/NgnPhamGiaHuy/mock-interview-platform}{MockInter – AI Powered Mock Interview Platform}}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Developed an AI-driven web application that simulates realistic job interviews, allowing users to practice through voice conversations and receive instant, data-driven performance feedback.
    \item Engineered a real-time, conversational AI interviewer by integrating Google's Generative AI for question logic and Vapi.ai for seamless voice interaction, creating an immersive practice experience.
    \item Implemented a secure authentication and user data management system using Firebase Auth and Firestore to track interview history, store performance metrics, and visualize user progress over time.
    \item Designed and built a responsive and interactive user interface with Next.js, React, and TailwindCSS, ensuring an intuitive experience across all devices.
    \item Architected a modular frontend with TypeScript to ensure type safety and scalability, separating concerns for API services, UI components, and state management.
\end{itemize}
\textbf{\href{https://github.com/NgnPhamGiaHuy/gemini-latex-enhancer}{Gemini LaTeX Enhancer – AI‑assisted CV enhancement with LaTeX outputs}}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
    \item Engineered a full-stack application with a decoupled Next.js frontend and FastAPI backend to provide a seamless, multi-step workflow for AI-driven CV customization.
    \item Integrated the Google Gemini API to perform deep content analysis, generating targeted suggestions to align CV content with job requirements and significantly reduce manual rewriting time.
    \item Implemented a robust batch processing system, enabling users to tailor a single CV against multiple job descriptions from a CSV upload, automating a highly repetitive and time-consuming task.
    \item Developed a backend service utilizing lualatex for automated LaTeX validation and PDF compilation, ensuring consistent, professional-grade document outputs and eliminating manual build steps.
    \item Designed asynchronous task handling with real-time progress tracking and secure file management to deliver a reliable and transparent user experience during intensive processing operations.
\end{itemize}

%---------- Skills ----------
\section*{Skills}
\textbf{Core Concepts:} Object-Oriented Programming (OOP), RESTful APIs, Agile Methodologies.\\
\textbf{Languages \& Frameworks:} JavaScript (ES6+), Python, React.js, Node.js, Next.js, Express.js, Flask, HTML, CSS.\\
\textbf{Databases:} MySQL (SQL), MongoDB.\\
\textbf{Developer Tools:} Git, Docker, Postman, Figma.\\
\textbf{Familiar With:} TypeScript, Redux, Tailwind CSS, WordPress.

%---------- Languages ----------
\section*{Languages}
\textbf{English:} Full Professional Proficiency (IELTS 6.5).\\
\textbf{German:} Elementary Proficiency.

\end{document}